Decoupled Fallback: A Portable Single-Pass GPU Scan

### 2025-02-08 paper.tex
Remove dot product hack, make Clang recommended compiler.

\subsubsection{Software Requirements}
\begin{itemize}
  \item Git
  \item CMake 3.10.2+ or another C++ build tool
  \item C++17-compliant compiler
  \item Python for fetching dependencies
\end{itemize}

\subsection{Building}
Although native WebGPU is supported on various operating systems—most notably Windows, macOS, and Linux—this section will focus on building it in Unix-like environments for the sake of brevity, using CMake as the example build tool.

@@

  \item Build and install Dawn with your build tool and compiler of choice:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cd dawn
cmake -S . -B out/Release \
  -DDAWN_FETCH_DEPENDENCIES=ON \
  -DDAWN_ENABLE_INSTALL=ON \
  -DCMAKE_BUILD_TYPE=Release \
  -DDAWN_BUILD_TESTS=OFF \
  -DDAWN_BUILD_SAMPLES=OFF \
  -DTINT_BUILD_TESTS=OFF \
  -DTINT_BUILD_CMD_TOOLS=OFF

@@

  \item Build the artifact:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cmake -S . -B out/Release \
  -DCMAKE_BUILD_TYPE=Release
  \end{lstlisting}

>>>>

\subsubsection{Software Requirements}
\begin{itemize}
  \item Git
  \item CMake 3.10.2+ or another C++ build tool
  \item C++17-compliant compiler (Clang recommended)
  \item Python for fetching dependencies
\end{itemize}

\subsection{Building}
Although native WebGPU is supported on various operating systems—most notably Windows, macOS, and Linux—this section will focus on building it in Unix-like environments for the sake of brevity, using CMake as the example build tool, and Clang++ as the example compiler.

@@

  \item Build and install Dawn:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cd dawn
cmake -S . -B out/Release \
  -DDAWN_FETCH_DEPENDENCIES=ON \
  -DDAWN_ENABLE_INSTALL=ON \
  -DCMAKE_BUILD_TYPE=Release \
  -DDAWN_BUILD_TESTS=OFF \
  -DDAWN_BUILD_SAMPLES=OFF \
  -DTINT_BUILD_TESTS=OFF \
  -DTINT_BUILD_CMD_TOOLS=OFF \
  -DCMAKE_CXX_COMPILER=clang++

@@

  \item Build the artifact:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cmake -S . -B out/Release \
  -DCMAKE_BUILD_TYPE=Release \
  -DCMAKE_CXX_COMPILER=clang++
  \end{lstlisting}
